---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# The Role of Fish Feces for Nutrient Cycling on Coral Reefs

<!-- badges: start -->
<!-- badges: end -->

The goal of this project is to reproduce all results and figures presented in the paper "The Role of Fish Feces for Nutrient Cycling on Coral Reefs", currently under revision at **Oikos**.
The project uses [targets](https://docs.ropensci.org/targets/), a pipeline tool for statistics and data science in R. 
Packages needed to reproduce this analysis and code to install them can be found in [make.R](make.R). 


## Content

The directory contains:

  - [:file\_folder: R](/R): Folder containing all functions, packages
    and drake plan.  
    \- **functions\_wrangling.R**: Contains functions to prepare the
    data for analyses.  
    \- **functions.R**: Contains functions used to reproduce
    analysis.  
    \- **functions\_plots.R**: Contains functions to create figures
    presenting the results.  
  - [:file\_folder: data](/data): Folder containing all data.
  - [:file\_folder: output](/text): All output including results and figures
    for publication.
  - _targets.R File containing workflow
  - make.R File: Script to run the whole project.
  
  
  
## Session info

```{r, echo=F}
sessionInfo()
```

